Reply to: 2022-05603 Intentional release of native species undermines ecological stability

### 2022-10-22 rmd/manuscript.Rmd
rmd

---
title: "Intentional release of native species undermines ecological stability"
output:
  bookdown::pdf_document2:
   latex_engine: xelatex
   toc: false
   number_sections: false
  #bookdown::word_document2:
  # reference_docx: word_format.docx
csl: https://www.zotero.org/styles/pnas
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile,
                          encoding = encoding, 
                          output_dir = "document_output")
      })
bibliography: reference.bib
fontsize: 11pt
mainfont: "Times New Roman"
header-includes:
  - \usepackage{lineno}
  - \linenumbers
---

@@

When carrying capacity was small ($K=$ `r min(list_param[[2]]$k)`), our model predicted a destabilizing effect of intentional release on ecological communities as illustrated by increased CV with increasing numbers of releases (**Figure** \@ref(fig:figure-layout)**A**). This pattern stemmed mainly from the reduced mean of the total community density, and both enhanced and unenhanced species groups were responsible (**Figure** \@ref(fig:figure-layout)**A**). The enhanced species decreased because release induced the negative competitive effect exceeding the reproductive contribution of released individuals, as reported in a previous theoretical study [@satakeStockingCaptivebredFish2012]. Meanwhile, interspecific competition reduced the unenhanced species, resulting in fewer persisting species (**Figure** \@ref(fig:figure-layout)**A**). Combined, the total community density decreased more sharply than individual species groups (**Figure** \@ref(fig:figure-layout)**A**). The SDs showed a similar trend, but the relationship was flatter at the community level (**Figure** \@ref(fig:figure-layout)**A**). Since a CV is a ratio of an SD to a mean, the steeper decline of the mean community density led to the increased CV. These patterns were qualitatively similar across ecological contexts with the low carrying capacity (**Figures S3 -- S6**), but except for the scenario in which the enhanced species exhibits chaos ($r_1=$ `r max(list_param[[2]]$r1)`).

>>>>

---
title: "Intentional release of native species undermines ecological stability"
output:
  bookdown::pdf_document2:
   latex_engine: xelatex
   toc: false
   number_sections: false
  #bookdown::word_document2:
  # reference_docx: word_format.docx
  # number_sections: false
csl: https://www.zotero.org/styles/pnas
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile,
                          encoding = encoding, 
                          output_dir = "document_output")
      })
bibliography: reference.bib
fontsize: 11pt
mainfont: "Times New Roman"
header-includes:
  - \usepackage{lineno}
  - \linenumbers
---

@@

When small carrying capacity was combined with a low to modest intrinsic growth rate ($K=$ `r min(list_param[[2]]$k)`, $r_1 \le 2.5$), our model predicted a destabilizing effect of intentional release on ecological communities, as illustrated by increased CV with increasing numbers of releases (**Figure** \@ref(fig:figure-layout)**A**). This pattern stemmed mainly from the reduced mean of the total community density, and both enhanced and unenhanced species groups were responsible (**Figure** \@ref(fig:figure-layout)**A**). The enhanced species decreased because release induced the negative competitive effect exceeding the reproductive contribution of released individuals, as reported in a previous theoretical study [@satakeStockingCaptivebredFish2012]. Meanwhile, interspecific competition reduced the unenhanced species, resulting in fewer persisting species (**Figure** \@ref(fig:figure-layout)**A**). Combined, the total community density decreased more sharply than individual species groups (**Figure** \@ref(fig:figure-layout)**A**). The SDs showed a similar trend, but the relationship was flatter at the community level (**Figure** \@ref(fig:figure-layout)**A**). Since a CV is a ratio of an SD to a mean, the steeper decline of the mean community density led to the increased CV. These patterns were qualitatively similar across ecological contexts with the low carrying capacity (**Figures S3 -- S6**), but except for the scenario in which the enhanced species exhibits chaos ($r_1=$ `r max(list_param[[2]]$r1)`).

### 2022-10-22 rmd/reply_r1.Rmd
rmd

Thank you for allowing us to revise our manuscript. The comments were very helpful in improving our manuscript. When revising the manuscript, we have put a particular emphasis on the following points:

1.  **Improve the Introduction and implications**: both reviewers noted an absence of context in the previous manuscript. We agree with this comment. We revised the text to contextualize our work better. In particular, we have carefully reviewed cases to which our findings may apply and discussed the relevance of our work to those systems.
2.  **Two-species simulation.** The editor suggested including a two-species simulation to guide the full community model. We appreciated this suggestion and were able to draw deeper insights into our theoretical analysis. At the same time, this improvement helped address the concern raised by reviewer 2 (they pointed out the lack of depth in theoretical analysis). We revised the Methods and Results following this change. In particular, we removed the old sensitivity analysis as it was redundant with two-species simulations.
3.  **Ecological interpretation of our empirical results (i.e., masu salmon system).** The reviewers and editor pointed out that the interpretation of our empirical analysis is superficial; we agree with this comment. We have enriched the text pertinent to this issue. We have greatly increased the number of citations and discussed possible mechanisms (e.g., diet overlap, exploitative competition) that may produce the observed patterns more carefully. In particular, we have added a new Ricker model analysis for empirical data to estimate competition coefficients in stream fish communities. The estimated parameter indicated that competition among species certainly exists.
4.  **Life history of masu salmon.** Lastly, we enriched the text for the life history of masu salmon and how release programs for this species are operated.

@@

> Agreed. We followed your guidance to improve the Introduction and Discussion (**paragraph L185 --, paragraph L209 --**). In short, we have clarified the following point:
>
> Introduction -- We have included representative works that report the scale of intentional release for commercial and recreational species. The release programs included plants, insects, mollusks, crustaceans, fish, birds, and others. The magnitude was enormous, releasing several tens of thousands to \> 10 millions of individuals annually. Thus, our system certainly represents a typical scenario of release programs (our program releases 0.24 million fish per year at the most intense watershed).
>
> Discussion -- Given the scale of other release programs, our results should represent a conservative estimate of community-level impacts. In addition, many programs release individuals into "unsuitable" habitats to aid declining populations -- these programs are likely to cause the destabilizing effect of the intentional release because the carrying capacities of such habitats are likely compromised. We have clarified this point in the revised manuscript.
>
> Discussion -- We have also clarified that our findings align with previous work on other hatchery programs (including salmons and other fisheries). The decline of wild stocks has been repeatedly observed after intensive stocking (consistent with our theoretical predictions and empirical patterns). We have cited an important meta-analysis [@arakiHatcheryStockingHelp2010] along with several specific examples (e.g., pink salmon in Alaska, where \> 600 million fish year^-1^ are released).

@@

> This greatly helped improve our manuscript, making the results relevant to other systems. We included more information on other salmon and fishery release programs (**paragraph L185 --**).

>>>>

This is a re-submission of a manuscript: "2022­05603 *Intentional release of native species undermines ecological stability.*" Thank you for allowing us to revise our manuscript. The comments were very helpful in improving our manuscript. When revising the manuscript, we have put a particular emphasis on the following points:

1.  **Improve the Introduction and broad implications**: both reviewers noted an absence of context in the previous manuscript. We agree with this comment. We revised the text to contextualize our work better. In particular, we have carefully reviewed cases to which our findings may apply and discussed the relevance of our work to those systems.
2.  **Two-species simulation.** The editor suggested including a two-species simulation to guide the full community model. We appreciated this suggestion and were able to draw deeper insights into our theoretical analysis. At the same time, this improvement helped address the concern raised by reviewer 2 (they pointed out the lack of depth in theoretical analysis). We revised the Methods and Results following this change. In particular, we removed the old sensitivity analysis as it was redundant with two-species simulations.
3.  **Ecological interpretation of our empirical results (i.e., masu salmon system).** The reviewers and editor pointed out that the interpretation of our empirical analysis is superficial; we agree with this comment. We have enriched the text pertinent to this issue. We have greatly increased the number of citations and discussed possible mechanisms (e.g., diet overlap, exploitative competition) that may produce the observed patterns more carefully. In particular, we have added a new Ricker model analysis for empirical data to estimate competition coefficients in stream fish communities. The estimated parameter indicated that competition among species certainly exists.
4.  **Life history of masu salmon.** Lastly, we enriched the text for the life history of masu salmon and how release programs for this species are operated.

@@

> Agreed. We followed your guidance to improve the Introduction and Discussion (**paragraph L186 --, paragraph L210 --**). In short, we have clarified the following point:
>
> Introduction -- We have included representative works that report the scale of intentional release for commercial and recreational species. The release programs included plants, insects, mollusks, crustaceans, fish, birds, and others. The magnitude was enormous, releasing several tens of thousands to \> 10 millions of individuals annually. Thus, our system certainly represents a typical scenario of release programs (our program releases 0.24 million fish per year at the most intense watershed).
>
> Discussion -- Given the scale of other release programs, our results should represent a conservative estimate of community-level impacts. In addition, many programs release individuals into "unsuitable" habitats to aid declining populations -- these programs are likely to cause the destabilizing effect of the intentional release because the carrying capacities of such habitats are likely compromised. We have clarified this point in the revised manuscript.
>
> Discussion -- We have also clarified that our findings align with previous work on other hatchery programs (including salmons and other fisheries). The decline of wild stocks has been repeatedly observed after intensive stocking (consistent with our theoretical predictions and empirical patterns). We have cited an important meta-analysis [@arakiHatcheryStockingHelp2010] along with several specific examples (e.g., pink salmon in Alaska, where \> 600 million fish year^-1^ are released).

@@

> This greatly helped improve our manuscript, making the results relevant to other systems. We included more information on other salmon and fishery release programs (**paragraph L186 --**).

### 2022-10-22 rmd/supporting_info.Rmd
Update supporting_info.Rmd
rmd

We subsequently analyzed a whole community model with 10 species using important parameter combinations identified in the two-species simulation: intrinsic growth of enhanced species ($r_1 =$ `r unique(list_param[[2]]$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(list_param[[2]]$alpha)`), carrying capacity ($K=$ `r unique(list_param[[2]]$k)`). We also varied relative fitness of captive-bred individuals ($f_R=$ `r unique(list_param[[2]]$phi)`) as this is a common interest in captive-breeding programs. Meanwhile, we fixed values of the following parameters: the number of species ($S=$ `r unique(list_param[[2]]$n_species)`), maximum intrinsic growth rate of unenhanced species ($r_{max}=$ `r unique(list_param[[2]]$r_max)`), and environmental stochasticity ($\sigma_{\varepsilon}=$ `r unique(list_param[[2]]$sd_env)`). This simulation setup resulted in `r nrow(list_param[[2]])` sets of parameter combinations.

@@

See Durante [@duranteNoteMultiplicativeGamma2017] for multiplicative gamma priors.

>>>>

We subsequently analyzed a whole community model with 10 species using important parameter combinations identified in the two-species simulation: intrinsic growth of enhanced species ($r_1 =$ `r unique(list_param[[2]]$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(list_param[[2]]$alpha)`), carrying capacity ($K=$ `r unique(list_param[[2]]$k)`). We also varied relative fitness of captive-bred individuals ($f_R=$ `r unique(list_param[[2]]$phi)`) as this is a common interest in captive-breeding programs. Meanwhile, we fixed values of the following parameters: the number of species ($S=$ `r unique(list_param[[2]]$n_species)`), maximum intrinsic growth rate of unenhanced species ($r_{max}=$ `r unique(list_param[[2]]$r_max)`), and environmental stochasticity ($\sigma_{\varepsilon}=$ `r unique(list_param[[2]]$sd_env)`). We used $r_{max}=$ `r unique(list_param[[2]]$r_max)` because the intrinsic growth rate higher than this value was rarely observed in nature [@myersMaximumReproductiveRate1999]. This simulation setup resulted in `r nrow(list_param[[2]])` sets of parameter combinations.

@@

Note: see Durante [@duranteNoteMultiplicativeGamma2017] for multiplicative gamma priors.
